Objective-First Design of High-Efficiency, Small-Footprint Couplers Between Arbitrary Nanophotonic Waveguide Modes

### 2012-01-10 presentations/ob1_wg_paper/paper.tex
Submitted to opex for the second time.

\begin{document}
\title{High-Efficiency, Small-Footprint Couplers Between 
    Arbitrary Nanophotonic Waveguide Modes}
\author{Jesse Lu and Jelena Vu\v{c}kovi\'{c}}
\address{Stanford University, Stanford, California, USA.}
\email{jesselu@stanford.edu}

\maketitle
\begin{abstract}
We develop an algorithm for designing
    high efficiency ($\sim$98\%), 
    small-footprint (1.5-4 square vacuum wavelengths)
    couplers between arbitrary nanophotonic waveguide modes
    in two dimensions.
Our ``objective-first'' method is
    computationally fast (15 minutes on a single-core personal computer), 
    requires no trial-and-error, and
    does not require guessing a good starting design.
We demonstrate designs for various coupling problems which suggest 
    that our method allows for the design of any 
    single-mode, linear optical device.
\end{abstract}
\ocis{230.75370, 130.3990.}

@@

The motivation behind this formulation is two-fold.
First, to arrive at a locally-optimal design rapidly 
    by allowing $x$ and $p$ to vary independently, 
    as opposed to Eq.~\ref{eq:adj}
    where the value of $x$ is completely dependent on $p$.
Second, to increase the likelihood of arriving at a high efficiency design
    by forcibly imposing $f(x) = 0$,
    and thereby circumventing any local optima consisting of
    low-performance devices.

@@

>>>>

\begin{document}
\title{Objective-First Design of 
    High-Efficiency, Small-Footprint Couplers Between 
    Arbitrary Nanophotonic Waveguide Modes}
\author{Jesse Lu and Jelena Vu\v{c}kovi\'{c}}
\address{Stanford University, Stanford, California, USA.}
\email{jesselu@stanford.edu}

\maketitle
\begin{abstract}
We present an algorithm for designing
    high efficiency ($\sim$98\%), 
    small-footprint (1.5-4 square vacuum wavelengths)
    couplers between arbitrary nanophotonic waveguide modes
    in two dimensions.
Our ``objective-first'' method is
    computationally fast (15 minutes on a single-core personal computer), 
    requires no trial-and-error, and
    does not require guessing a good starting design.
We demonstrate designs for various coupling problems which suggest 
    that our method allows for the design of any 
    single-mode, linear optical device.
\end{abstract}
\ocis{230.75370, 130.3990.}

@@

The motivation behind this formulation is two-fold.
First, this approach allows is to arrive at a locally-optimal design rapidly 
    by allowing $x$ and $p$ to vary independently, 
    as opposed to Eq.~\ref{eq:adj}
    where the value of $x$ is completely dependent on $p$.
Second, it enables an increase in the likelihood of 
    arriving at a high efficiency design
    by forcibly imposing $f(x) = 0$,
    and thereby circumvents any local optima consisting of
    low-performance devices.

@@

In the appendix, we further demonstrate the generality of our method
    by presenting several additional examples including
    \begin{enumerate}
    \item coupling between all four modes of a wide dielectric waveguide;
    \item coupling from a wide, low-index waveguide to the output waveguides in 
        Figs~\ref{fig:mode}-\ref{fig:wire}; and
    \item coupling to selected channels of a set of five plasmonic waveguides.
    \end{enumerate}
